### 2025-09-11 docs/test.tex
minor changes
Small fix

\subsubsection{Households with Wealthier Parents Are Less Delinquent} 
One potential roadblock to maintaining ownership is mortgage delinquency, as missed payments can lead to distressed or forced sales. I show that households with wealthier parents are less likely to fall behind on their mortgages, despite purchasing more expensive homes. The PSID has collected mortgage delinquency data since 2009; about 2\% of owners aged 25 to 44 report being behind.

@@

\textit{Preferences and Altruism:} Parents and children have time-separable expected utility with a discount factor of $\beta$. Households maximize expected utility, and the per-period utility function for children is
\begin{equation}
U_c(c_c,h_c) = u(c_c,h_c) = \frac{\left(c_c^\xi s(h_c)^{1-\xi}\right)^{1-\gamma}-1}{1-\gamma},
\end{equation}
where $c$ is consumption, $h$ is housing, $\gamma$ is the coefficient of relative risk aversion, and $\xi$ measures the relative importance of consumption to housing services. The within-period Cobb-Douglas aggregator imposes a constant desired expenditure share on housing services, roughly consistent with empirical evidence (e.g., \cite{davis2011household}). The function $s(h)$ allows utility to depend on ownership:
\begin{equation}
s(h) = \begin{cases}
h & \text{ if renting}, \\
\chi h & \text{ if owning}.
\end{cases}
\end{equation}
The parameter $\chi$ measures the owner-occupied utility premium, reflecting any additional benefits derived from owner-occupation, such as stability or ownership rights.

>>>>

\subsubsection{Households with Wealthier Parents Are Less Delinquent} 
One roadblock to maintaining ownership is mortgage delinquency, as missed payments can lead to distressed or forced sales. I show that households with wealthier parents are less likely to fall behind on their mortgages, despite purchasing more expensive homes. The PSID has collected mortgage delinquency data since 2009; about 2\% of owners aged 25 to 44 report being behind.

@@

\textit{Preferences and Altruism:} Parents and children have time-separable expected utility with a discount factor of $\beta$. Households maximize expected utility, and the per-period utility function for children is
\begin{equation}
U_c(c_c,h_c) = u(c_c,h_c) = \frac{\left(c_c^\xi s(h_c)^{1-\xi}\right)^{1-\gamma}-1}{1-\gamma},
\end{equation}
where $c$ is consumption, $h$ is housing, $\gamma$ is the coefficient of relative risk aversion, and $\xi$ measures the relative importance of consumption to housing services. The within-period Cobb-Douglas aggregator imposes a constant desired expenditure share on housing services, roughly consistent with empirical evidence (e.g., \cite{davis2011household}). The function $s(h)$ allows utility to depend on ownership:
\begin{equation}
s(h) = \begin{cases}
h & \text{ if renting}, \\
\chi \times h & \text{ if owning}.
\end{cases}
\end{equation}
The parameter $\chi$ measures the owner-occupied utility premium, reflecting any additional benefits derived from owner-occupation, such as stability or ownership rights.
